---
title: "vignette"
author: "Han Xia,Can Wang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction

The **lab5** package provides functions for fetching data from the Kolada API. Kolada is a Swedish open data platform that offers various datasets for research, policy-making, and public information. With this package, you can easily retrieve data from Kolada by either searching for specific terms or fetching data for a given year.

```{r setup}

library(lab5)
library(httr)
library(jsonlite)
```
1. get_api: Fetch Data Based on a Search Term
get_api(search, api_key)

This function allows you to search for specific terms in the Kolada database and fetch the corresponding data. You will need an API key to use this function.

2. get_kolada_data: Fetch Data for a Specific Year
get_kolada_data(year)

This function retrieves data for a specified year (between 1900 and 2100) from the Kolada API.
For example:
```{r example}
# Fetch data for the year 2021
data_2021 <- get_kolada_data(2021)

# Display a summary of the data
print(data_2021)

# Example of an invalid year
invalid_data <- get_kolada_data(1899)  # This will stop with an error
```